Fluent statistical computing interfaces for biological data analysis

### 2020-07-24 Rmd/05-embeddings.Rmd
add reference to tSNE!

In the following section, we provide a brief overview of the goals of DR
methods with respect to the data analyst, in addition to their high level the
mathematical details. Here we restrict our attention to two recent methods that
are commonly used in the literature: t-distributed stochastic neighbour embedding 
(t-SNE) and uniform manifold alignment and projection (UMAP); however we do 
mention several other techniques.

@@

The t-SNE algorithm estimates
the pair-wise similarity of (Euclidean) distances of points in a high
dimensional space using a Gaussian distribution and then estimates a
configuration in the low dimensional embedding space by modelling similarities
using a t-distribution with 1 degree of freedom. There are several subtleties
to the to use of the algorithm that are revealed by stepping through its
machinery.

>>>>

In the following section, we provide a brief overview of the goals of DR
methods with respect to the data analyst, in addition to their high level the
mathematical details. Here we restrict our attention to two recent methods that
are commonly used in the literature: t-distributed stochastic neighbour embedding 
(t-SNE) and uniform manifold alignment and projection (UMAP); however we do 
mention several other techniques [@Maaten2008-sk; @McInnes2018-co].

@@

The t-SNE algorithm estimates
the pair-wise similarity of (Euclidean) distances of points in a high
dimensional space using a Gaussian distribution and then estimates a
configuration in the low dimensional embedding space by modelling similarities
using a t-distribution with 1 degree of freedom [@Maaten2008-sk]. There are several subtleties
to the to use of the algorithm that are revealed by stepping through its
machinery.
